Accelerated evolution of convective simulations

### 2018-06-12 referee_process/first_submission/referee_response.tex

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[aps, 11pt, singlecolumn]{revtex4-1} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{natbib}
\bibliographystyle{apsrev}
\usepackage{setspace}

\begin{document}
\newenvironment{myquotation}{
\begin{quotation}
\itshape
}{ 
\end{quotation}
}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
\noindent
Dear Eckart, other PRFluids editors, and anonymous referees,
$\,$\newline

\begin{singlespace}
We return a new draft of our manuscript, ``Accelerated evolution in
convective simulations,'' addressing the concerns of the referee reports.
We would like to point out a few major changes in this version of the manuscript.
A new section, ``Computational time-savings of AE'' has been added after the
results section and before the conclusion section. In this section, we directly
compare the computational cost of AE and SE for select simulations and we discuss
the computational benefits of AE.  Furthermore, the final section of our paper
is now titled ``Discussion \& Conclusions;'' we have removed a vast amount
of speculation regarding extensions of AE from this section and have added
a paragraph containing some caveats regarding challenges that users will face in
extending AE to more difficult systems.  In addition to these changes in the text,
we have added a new Fig. 2 which compares the evolution of Nu and the
mean temperature in AE and SE, and we have added some accompanying text for this
figure to the results section.  Small changes in the text throughout the paper have
been made for clarity where these changes were requested by the reports.

We feel that the clarity and scientific content of the paper have been greatly
improved by the referee reports, and we thank the referees for their honest 
critiques and attention to detail. We hope that the changes made have clarified
and cleaned up the areas of concern raised in both referee reports.  Below we
include our responses to the reports. The original text of the reports is included
in italics, and our responses follow inline in unitalicized blocks.

@@

$\,$\newline
\noindent
Sincerely,

Evan H. Anders, Benjamin P. Brown, \& Jeffrey S. Oishi

%\end{singlespace}

\newpage
\noindent
\Large{\textbf{Response to first referee:}}\newline$\,$\newline\indent

\begin{myquotation}
This paper describes a technique for accelerating the convergence to
thermal equilibrium in convective DNS simulations where such
convergence from an initial conductive state would be long. The
technique is essentially to evolve a DNS for for a while, collect the
background state non-equilibrium fluxes, and then solve a mean field
boundary value problem with scaled version of these fluxes for a new
background state in thermal equilibrium, then use this to restart the
DNS. These, or very similar techniques, have been used by many in the
past, although to my knowledge, as the authors here also claim, they
have not been explicitly written down in a paper. The authors have
gone to the trouble of doing this, not only providing a fairly
detailed prescription of the technique, but also some evidence of its
usefulness, albeit in a very simple case where it will definitely work
which is perhaps not totally representative. I guess I think this
paper is overall worthwhile, since it provides a place for newcomers
to the business to find some potentially time-saving help, even though
the ideas are not original. I think the most important issue with this
paper is that its claims of more universal applicability are somewhat
naive. I would suggest they temper these assertions substantially.

Basic questions:

How confident can one be that the BVP puts you closer to a nonlinear
saturated state than where you were? For example, in highly nonlinear
(turbulent) problems, there may be multiple states, maybe even
multiple stable states, with different background properties. Is it
possible to guarantee that you are not putting the system into an
equilibrium but unstable state, from which an equally long evolution
to a stable state is required? For the simple problems shown here,
this is perhaps not likely, but for very high degrees of turbulence,
or situations where unknown instabilities may exist, this process may
not be so successful perhaps? This is again a factor in my hesitation
about the total applicability of this technique across many problems
beyond the one the authors present.
\end{myquotation}
We are confident that the BVP puts us closer to a nonlinear saturated state
than we were before. It is true that there may be multiple stable states, and there
is no guarantee that the BVP puts the solution into the same stable state as
SE. We have mentioned this in our conclusion.

@@

I don’t understand ``$10^{3+2/3}$''? Why is written like this?
\end{myquotation}
To determine the Ra of our simulations, we take even sized steps in log space
(3 per decade). We have changed 3 + 2/3 to 3.67 for easier reading.

\begin{myquotation}
I am not convinced that the whole ``2D and 3D scaling laws'' section
adds anything at all to this paper. It shows that this technique can
be used but so does the single example that is interrupted by this
piece. It is somewhat interesting for the scaling laws found
themselves, but it sounds like this should be in a different paper
because there is not enough explanation to understand things totally
here. I feel like the examples before and after this section are
sufficient to make the point about the AE scheme.
\end{myquotation}
We feel that it is important to show that AE works across some swath of parameter
space, in order to demonstrate its robustness for the problem presented here.
We have trimmed the text of the scaling laws section and reduced speculation in
order to keep the paper on topic. We have also replaced Re with Pe in this
section in order to reinforce the point that we are interested in high Pe
convection (since Pr = 1, Re = Pe numerically, so only labels have changed).

\begin{myquotation}
When discussing the PDFs, the author refer to the ``modes" of the PDF?
This sounds a bit odd to me. Do they mean the peaks? The phrase
``temperature fluctuations off of the modes'' is particularly baffling!
\end{myquotation}
We have replaced ``modes'' with ``maxima'' for clarity.

\begin{myquotation}
The fact that the mean temperature profile is off by a constant factor
almost everywhere is a bit disturbing, even if the factor is small.
Does continued iteration of AE not get rid of this? If not, then this
is significant, because it would take a thermal relaxation time again
to correct this issue.
\end{myquotation}
We have added a paragraph to the ``accelerated evolution recipe'' appendix.
In it, we discuss the fact that AE can be iteratively solved until you converge
to a desired fractional percentage, and that we were only aiming for O(1\%) in this
paper.  It is true that it will likely take a thermal relaxation time to evolve 
from the 1\% off state to the true state, but that slow evolution does not
appreciably change the dynamics.

\begin{myquotation}
I felt like I wanted a section at the end of this section that
described how much the AE saved in computational time and wall time
over SE. There is a bit of it here, and some of it in the discussion,
and some more details in the appendix, which seems a bit scattered. I
would be tempted to agglomerate it all here in a separate section.
\end{myquotation}
We have added a new section V., ``Computational Time-savings of AE.''
We have combined the relevant information from the results section and the 
conclusion section previously here, and we have added some information on a few
additional runs in a new table.

@@

The example performed was the most likely to succeed. The 2D cases
were essentially rolls. Were the 3D cases still essentially 2D rolls
too (since the scalings came out the same)? What about larger aspect
ratio and more turbulence cases where the dynamics would be more
complex? Keeping things smooth certainly enhances the likelihood of a
simple scaling of the nonlinear fluxes working.

I think the projections for more complicated problems mentioned are
naive. If there is any nonlinear adjustment to the convective region,
e.g. penetrative convection, then the technique is far less likely to
be simply successful in the current form. The assumption of fully
convective and thermal boundary layers remaining in place is a big
one, and this is not really acknowledged. The authors do mention
penetrative convection and do indeed say that only a stiff case would
work under these premises, but this is a bit hidden, I think, and
needs to be emphasized more. For example, the penetrative ice-water
problem even in Boussinesq would not work well with this technique I
think, since the penetrative region can deepen dramatically, and
adjust the radiative flux to match the substantially changed
convective flux.

Furthermore, the compressible case is much more danger prone than
envisioned here. I suspect that in the iteration to accelerate, any
mismatch in the fluctuations and the estimated means in the DNS will
lead to major transients in the form of sound waves, which can totally
destroy a compressible evolution by reducing the tilmestep
substantially, so this technique may have drawbacks if there is not
filtering of sound waves somehow. The authors have glossed over these
problems in their eagerness to extol the virtues of their scheme.

I think the claims of this method working in many more situations need
to be examined more thoroughly before being made so boldly here.
\end{myquotation}
We agree that our intial conclusion section was over-eager. We have 
greatly reduced the amount of text spent on speculation surrounding
extensions of the AE method, and have added a paragraph warning the
reader that not all extensions will be as simple (or guaranteed to work)
as the case studied here.

\newpage
\noindent
\Large{\textbf{Response to second referee:}}\newline$\,$\newline\indent
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\item The authors should provide clarification on what the following terms mean: ``thermal equilibration'', ``thermally relaxed'', and ``thermal convergence''. Also, are these terms related to statistically steady state?
\end{enumerate}
\end{myquotation}
All three of these phrases are equivalent, and we have replaced all mentions of
thermal equilibration, relaxation, and thermal convergence with ``thermal
equilibration'' or ``thermally equilibrated'' throughout the paper. This term
is explained in pargraph 2 of the introduction.
\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{1}
\item What is the ``Kelvin-Helmholtz timescale''?
\end{enumerate}
\end{myquotation}
The Kelvin-Helmholtz timescale is 
$$
t_{\text{KH}} = \frac{E_g}{L},
$$
where $E_g$ is the gravitational energy in a system, and $L$ is the luminosity
(energy output / time). Basically it is a timescale that astronomers and
astrophysicists use to estimate the timescale of thermal evolution of a system 
(e.g., a star). Since the point we were trying to make is that ``the mean 
thermodynamic structure of the Sun evolves \emph{really} slowly,''
we have removed this jargon and said this more clearly in paragraph 2 of the intro.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{2}
\item The authors note that the bootstrapping method is susceptible to hysteresis effects. They should provide examples of where such effects have been observed.
\end{enumerate}
\end{myquotation}
We misspoke. We have not specifically seen hysteresis effects (nor have we seen
this in the literature).  We meant to say that in simulations where there are
multiple solution branches (e.g., a convective roll and a shearing solution),
bootstrapping a solution on one branch to different parameters with the same
solution branches will result in a solution on the 
same solution branch. Particularly, in our own
work in stratified atmospheres, atmospheres trend toward shearing states, and then
stay stuck in those states as we bootstrap to higher Ra.

We have corrected our error and made our meaning clearer.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{3}
\item It is true that direct numerical simulation of turbulent thermal convection is expensive. However, the highest Ra simulation run by Stevens et al. reaches a stationary state in a few hundreds of free-fall times. Hence, what is the necessity of running simulations for ``thousands or millions of free-fall times''?
\end{enumerate}
\end{myquotation}
We have added a new Fig. 2 to address this question. In general, the convective
flows and heat transport (e.g., Nu) reach their final, time-stationary mean
value very quickly (see panels (a) and (b) of Fig. 2). However, the thermal 
structure of the system can still be slowly evolving for long timescales
despite the flows being relatively statistically stationary. The purpose of
running for many, many free-fall times is to converge the thermal profile of
the domain to ensure that the full system is in a steady state.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{4}
\item Presumably, the most important step in the “Accelerated convergence method” involves decreasing the heat flux through the top boundary so as to match it with the heat flux at the bottom boundary. This is achieved by introducing a function $\xi(z) \equiv  F_B/F_{tot}$. The following questions arise:
\begin{enumerate}
\item What is the functional form of $\xi(z)$? And where does the z-dependence come from?
\item Here, $F_{tot}$ is not really a constant, but depends on time. Hence, $\xi(z)$ should also be a function of time.
\item The ``evolved'' quantities are obtained by multiplying $\langle u \times \omega \rangle$ and $F_E$ by $\xi(z)$. Can this construction be rigorously justified? I would like the authors to provide more details on how they arrived at this step.
\end{enumerate}
\end{enumerate}
\end{myquotation}

(a) In the simple case studied in this problem, where $F_B$ is constant in time
and space, the functional form of $\xi \propto F_{tot}^{-1}$, and depends only
on the fluxes of the convective system. Since $F_{tot}$ can
have a large z-dependence (e.g., Fig. 1b), $\xi$, too, has a z-dependence. 
$\xi$ is simply a height-dependent scaling that we use to appropriately
adjust our velocity, temperature, etc.

@@

(b) We have changed $\xi(z) \rightarrow \xi(z, t)$.

(c) Physically, $\xi$ is a scaling factor that tells us how much larger the flux
is in the interior than it should be. 
We assume that $F_{tot} \sim F_{conv} \sim w (T - \langle T \rangle )$.
As such, we assume that $\xi \propto (w^{-1/2}, (T - \langle T \rangle )^{-1/2})$,
and that scaling both the temperature fields and the temperature fluctuations 
around the mean profile will reduce the convective flux in the proper way.
We scale $\langle u\times \omega\rangle$ by $\xi$, as it is
nondimensionally of order $u^2 / L$, and so if the velocities must be multiplied
by $\sqrt{\xi}$, this term must be multiplied by $\xi$.

@@

We cannot rigorously derive $\xi$ from first principles. Its form, and the use of
it here, are the result of our experience and familiarity with convection.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{5}
\item The assumption that convection at early times occupies roughly the same volume as convection in the stationary state is acceptable. However, there is also the possibility that instead of decreasing the heat flux at the top one could increase it at the bottom? The boundary condition for T1 at the bottom surface is
$$
\frac{\partial T_1}{\partial z} = 0
$$
So, the imposed heat flux at the bottom is 0.
\end{enumerate}
\end{myquotation}
Our boundary condition is that \emph{fluctuations} in the temperature derivative at the
bottom of the domain are zero. Which is to say that 
$\partial T_0 / \partial z = -1 =$ constant. We could increase the heat flux at
the bottom to match the heat flux at the top, but in that case we would be solving
a different system with a different set of boundary conditions than the ones
studied here.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{6}
\item Could the authors construct plots of Nu vs. t (like in figure 2) for both AE and SE starting from t = 0? I would like to understand how Nu(t) evolves with time in the AE cases.
\end{enumerate}
\end{myquotation}
We have created this plot as part of a reponse to point 4. Please refer to the
new Fig. 2 in the text.

\begin{myquotation}
$\,$\\\vspace{-1.25cm}
\begin{enumerate}
\setcounter{enumi}{7}
\item I diasgree with the authors’ statement that “Previous studies in 2D convection may have avoided these time-varying Nu states by using bootstrapping techniques...” If one were to measure Nu(t) in the interior, then the sign of Nu would fluctuate between positive and negative. However, the time average would be always be positive. (This I know from my own work.)
\end{enumerate}
\end{myquotation}
The purpose of the previous Fig. 2 (now Fig. 3) was merely to show why we have
such large error bars on Nu in our Nu v. Ra plot (Fig. 4). Our aim is to show
the nature of the flow morphologies at times of high and low heat transport;
the instantaneous sign of Nu (positive or negative) is not what we are trying
to point out.

We have clarified the discussion around the scaling laws, as requested by the
other referee report. We have removed speculative statements which aimed to
compare the scaling law of Nu found here with Nu elsewhere in order to keep
the focus of our paper on AE rather than Nu scaling for our system setup.

### 2018-06-12 tex/bvp_paper.tex
so many changes
rough second draft of paper

Unfortunately, astrophysical convective systems are stiff in more than one 
timescale. Specifically, the Peclet number (Pe), the ratio of the thermal
diffusion timescale to the advective velocity timescale, is large.
This further stiffness arises as a result of the thermodynamic structure 
evolving over the course of thermal timescales, not the short dynamical advective
timescales. In order to reach thermal equilibration, a steady state in which
the thermal structure of the atmosphere is no longer evolving over time,
many dynamical timescales must be simulated.
Transport by convection is a highly nonlinear process,
and this makes addressing the stiffness much more challenging; even fully
implicit  methods remain bound by the nonlinear flow timescales
\cite{viallet&all2011, viallet&all2013, viallet&all2016}. 
Resolving dynamics in atmospheres which are sufficiently
thermally equilibrated remains a challenging problem.
Solar convection is a prime example of this phenomenon, as
dynamical timescales in the solar convective zone are relatively short 
(convection overturns every $\sim 5$ minutes at the solar surface)
compared to the Sun's thermal evolution timescale, which is O($10^7$) years
\cite{stix2003}.  
In such a system, it is impossible to resolve the convective dynamics while also
meaningfully evolving the thermal structure of the system using
traditional timestepping techniques alone.
As modern simulations aim to model natural, high-Pe convection
in the high-Rayleigh-number (Ra) regime,
the thermal diffusion timescale ($t_{\kappa}$, defined in section \ref{sec:ae}) 
becomes intractably large compared to dynamical timescales 
such as the freefall time ($t_{\text{ff}}$, defined in section \ref{sec:experiment})
\cite{anders&brown2017}, 
\begin{equation}
\frac{t_{\kappa}}{t_{\text{ff}}} \propto (\text{Ra})^{1/2}.
\end{equation}
Furthermore, as dynamical and thermal timescales separate, 
simulations become more turbulent. Capturing appropriately resolved
turbulent motions requires finer grid meshes and smaller timesteps.
Thus, the progression of simulations into the high-Ra
regime of natural convection is slowed by two simultaneous effects: timestepping
through a single convective overturn time becomes more computationally expensive
and the number of overturn times required for systems to reach thermal equilibration
grows.

@@

In order to adjust the temperature profle to achieve AE, we calculate the total flux,
F$_{\text{tot}} =$ F$_{\text{E}}$ + F$_{\kappa}$, and then derive the profiles
\begin{equation}
f_{\text{E}}(z) = \frac{\text{F}_{\text{E}}}{\text{F}_{\text{tot}}},\qquad
f_{\kappa}(z) = \frac{\text{F}_{\kappa}}{\text{F}_{\text{tot}}},
\label{eqn:bvp_ratios}
\end{equation}
which have the systematic asymmetries (Fig.~\ref{fig:time_trace}b) removed. These profiles describe which
parts of the atmosphere depend on convection to carry flux (where $f_{\text{E}}(z) = 1$
and $f_{\kappa}(z) = 0$).
We presume that the early convection occupies roughly the same volume as the evolved
convection, and thus that the extent of the early thermal boundary layers 
(where $f_{\kappa}(z) = 1$ and $f_{\text{E}}(z) = 0$) 
will not change significantly over the course of the atmosphere's evolution.
Under this assumption, in order to reach the converged state, 
the flux through the atmosphere must be decreased by some amount,
\begin{equation}
\xi(z) \equiv \frac{\text{F}_{\text{B}}}{\text{F}_{\text{tot}}},
\label{eqn:xi}
\end{equation}
where $\text{F}_{\text{B}} = \mathcal{P}$ is the amount of flux that enters the
bottom of the atmosphere.

@@

Thus, the AE method occurs in the following steps. First, we pause a convective simulation and
construct $\xi(z)$ from measured flux profiles in the convective domain.
We solve a 1D boundary value problem consisting of
Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
to obtain an evolved thermodynamic profile, and its corresponding conductive flux.
To consistently modify the convective enthalpy flux, we multiply both the velocity field,
$\bm{u}$, and the temperature perturbations around the mean profile, $T - \angles{T}_{x,y}$,
by $\sqrt{\xi}$; this diminishes the magnitude of these perturbations, and the
flux they carry, appropriately.
After adjusing the fields of a simulation in this manner, we continue timestepping forward.
For specifics on the precise implementation of the AE method, we refer
the reader to appendix \ref{appendix:recipe}.

%%%%%%%%%%%%
%%%%%%%%%%%
% RESULTS
%%%%%%%%%%%
%%%%%%%%%%%%
\section{Results}
\label{sec:results}
We study evolved standard evolution (SE) solutions whose supercriticalities ($S$) are 
$S \in (1, 10^5]$ in 2D and $S \in (1, 10^4]$ in
3D. We compare their properties to
accelerated evolution (AE) runs at $S \in (1, 10^7]$ in 2D and
$S \in (1, 10^4]$ in 3D.
We refer the reader to appendix \ref{appendix:run_table} for a full list of
simulations.

The Nusselt number (Nu) quantifies the efficiency of convective heat transport
and is defined as
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
\end{equation}
where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
The time evolution of Nu in AE and SE is compared to the mean temperature evolution
in Fig.~\ref{fig:nu_v_time}. The mean value of Nu evolves towards its final value
rapidly compared to the mean temperature. Thus, if Nu is the primary metric of 
the evolved flows being measured, it is unnecessary to run for a full thermal
time, and previous authors have taken advantage of this (CITE).
When $S < 10^{3.67}$ in 2D and for all runs in 3D, 
the evolved system is characterized by a time-stationary value of Nu, and is thus
in a state of constant convective heat transport.
At larger $S$ in 2D, the value of Nu varies significantly over time,
as shown by the time traces for $S = 10^5$ (top, left) and $S = 10^7$ (bottom, left) for two
AE runs in Fig.~\ref{fig:oscillating_plumes}. We find that these systems exhibit
large Nu during
states in which temperature fluctuations travel in their natural buoyant
direction (Fig.~\ref{fig:oscillating_plumes}, Ia \& IIa, where cold elements fall and hot elements rise).
However, when wrongly-signed temperature perturbations are entrained in an upflow or downflow
with oppositely signed fluid, Nu is suppressed (Fig.~\ref{fig:oscillating_plumes}, Ib and IIb, 
where warm fluid is pulled down by the downflow
lane, and cool fluid is drawn up by the upflow lane). High-transport and 
low-transport states exhibit smaller Nu fluctuations away from the 
mean once the system reaches thermal equilibrium (Fig. \ref{fig:nu_v_time}).
The plumes in these
systems naturally oscillate horizontally over time, switching between transport being dominated
by a counterclockwise cell, as pictured in Fig.~\ref{fig:oscillating_plumes}, and
a clockwise cell. Our choice of no-slip
boundary conditions prevents the fluid from entering a full domain shearing state 
\cite{goluskin&all2014}, and the
oscillatory nature of the plumes is stable. However, thanks to our choice of periodic
boundary conditions and despite the no-slip conditions, the full system of the
upflow and downflow plumes is free to slowly migrate to the left or right over time,
and we observe this phenomenon in our solutions.
The 2D SE simulations exhibit the same horizontally
oscillatory behavior as the AE solutions for the same initial conditions. 
This time-dependent behavior of Nu is not seen strongly in our 3D solutions,
however most 3D simulations we conducted were at low $S$ compared to the runs in
which this behavior was observed in 2D.

\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/nu_v_time.png}
\caption{Here we compare the time evolution of the mean temperature and the
Nusselt number for the 2D SE and AE run shown in Fig.~\ref{fig:time_trace}.
\label{fig:nu_v_time} }
\end{figure}

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
\caption{The time variation of the Nusselt number is shown for two AE cases at
$S = 10^5$ (top) and $S = 10^7$ (bottom). On the left, the instantaneous value of Nu
is shown as a function of time. On the right, temperature snapshots are shown for
Nu maxima (Ia \& IIa) and minima (Ib \& IIb). The suppressed value of Nu at the
minma arises from entrainment of fluid elements whose temperature perturbations
are wrongly signed (e.g., hot material going downwards and cold material going
upwards in Ib \& IIb). The colorbar scaling of panels Ia\&b are the same, as
are the scalings of panels IIa\&b. 
The minimum temperature is chosen by the fixed-temperature
boundary condition at the top, $T_{\text{top}} = -0.5$. The decreased range of
the colorbar scaling for
for IIa\&b was chosen to better display the convective dynamics.
\label{fig:oscillating_plumes} }
\end{figure}

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements of the Nusselt number (Nu), the
RMS Reynolds number (Re), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement and denote 2D (purple circles) and 3D (red stars). 
The run at $S = 10^5$ marked as a
black square is examined in more detail in Figs. \ref{fig:time_trace}, \ref{fig:oscillating_plumes},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
Vertical lines represent the standard deviation of the measurement,
and quantify natural variation over the averaging window. 
(a) Nu scales as Ra$^{1/5}$; at high $S$ in 2D the value of Nu fluctuates over time
(see Fig.~\ref{fig:oscillating_plumes}).  
(b) Re, which measures turbulence in the solution, scales as
Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at the fixed-temperature
top boundary is shown; this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
Relative error for measurements of (d) Nu, (e) Re, and (f) $\angles{T} - T_{\text{top}}$ between 
AE solutions and SE solutions are shown.
The greyed area of the plots indicates the region in which only AE runs were
carried out due to computational expense. \label{fig:parameter_space_comparison} }
\end{figure}

>>>>

Unfortunately, astrophysical convective systems are stiff in more than one 
timescale. Specifically, the Peclet number (Pe), the ratio of the thermal
diffusion timescale to the advective velocity timescale, is large.
This further stiffness arises as a result of the thermodynamic structure 
evolving over the course of thermal timescales which are much larger than
the relevant dynamical advective
timescales. In order to reach thermal equilibration, a steady state in which
the thermal structure of the atmosphere is no longer evolving over time,
many dynamical timescales must be simulated.
Transport by convection is a highly nonlinear process,
and this makes addressing the stiffness much more challenging; even fully
implicit  methods remain bound by the nonlinear flow timescales
\cite{viallet&all2011, viallet&all2013, viallet&all2016}. 
Resolving dynamics in atmospheres which are sufficiently
thermally equilibrated remains a challenging problem.
Solar convection is a prime example of this phenomenon, as
dynamical timescales in the solar convective zone are relatively short 
(convection overturns every $\sim 5$ minutes at the solar surface)
compared to the Sun's thermal evolution timescale, which is O($10^7$) years
\cite{stix2003}.  
In such a system, it is impossible to resolve the convective dynamics while also
meaningfully evolving the thermal structure of the system using
traditional timestepping techniques alone.
As modern simulations aim to model natural, high-Pe convection
in the high-Rayleigh-number (Ra) regime,
the thermal diffusion timescale ($t_{\kappa}$, defined in section \ref{sec:ae}) 
becomes intractably large compared to dynamical timescales 
such as the freefall time ($t_{\text{ff}}$, defined in section \ref{sec:experiment})
\cite{anders&brown2017}, 
\begin{equation}
\frac{t_{\kappa}}{t_{\text{ff}}} \propto (\text{Ra})^{1/2}.
\end{equation}
Furthermore, as dynamical and thermal timescales separate, 
simulations become more turbulent. Capturing appropriately resolved
turbulent motions requires finer grid meshes and smaller timesteps.
Thus, the progression of simulations into the high-Ra
regime of natural convection is slowed by two simultaneous effects: timestepping
through a single convective overturn time becomes more computationally expensive
and the number of overturn times required for systems to reach thermal equilibration
grows.

@@

In order to adjust the temperature profle to achieve AE, we calculate the total flux,
F$_{\text{tot}} =$ F$_{\text{E}}$ + F$_{\kappa}$, and then derive the profiles
\begin{equation}
f_{\text{E}}(z) = \frac{\text{F}_{\text{E}}}{\text{F}_{\text{tot}}},\qquad
f_{\kappa}(z) = \frac{\text{F}_{\kappa}}{\text{F}_{\text{tot}}},
\label{eqn:bvp_ratios}
\end{equation}
which have the systematic asymmetries (Fig.~\ref{fig:time_trace}b) removed. These profiles describe which
parts of the atmosphere depend on convection to carry flux (where $f_{\text{E}}(z) = 1$
and $f_{\kappa}(z) = 0$).
We presume that the early convection occupies roughly the same volume as the evolved
convection, and thus that the extent of the early thermal boundary layers 
(where $f_{\kappa}(z) = 1$ and $f_{\text{E}}(z) = 0$) 
will not change significantly over the course of the atmosphere's evolution.
Under this assumption, in order to reach the converged state, 
the flux through the atmosphere must be decreased by some amount,
\begin{equation}
\xi(z,t) \equiv \frac{\text{F}_{\text{B}}}{\text{F}_{\text{tot}}},
\label{eqn:xi}
\end{equation}
where $\text{F}_{\text{B}} = \mathcal{P}$ is the amount of flux that enters the
bottom of the atmosphere. $\xi$ is a general depth-dependent scaling factor which
tells us roughly how much larger F$_\text{E}$ is in the interior than it should
be in the thermally equilibrated state.

@@

Thus, the AE method occurs in the following steps. First, we pause a convective simulation and
construct $\xi(z)$ from measured flux profiles in the convective domain.
We solve a 1D boundary value problem consisting of
Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
to obtain an evolved thermodynamic profile, and its corresponding conductive flux.
To consistently modify the convective enthalpy flux, we multiply both the velocity field,
$\bm{u}$, and the temperature perturbations around the mean profile, $T - \angles{T}_{x,y}$,
by $\sqrt{\xi}$; this diminishes the magnitude of these perturbations, and the
flux they carry, appropriately. This scaling of variables with $\sqrt{\xi}$ is also
the reason that we multiply $\angles{\bm{u}\times\bm{\omega}}_{x, y}$ by $\xi$
before solving for the evolved temperature profile.
After adjusing the fields of a simulation in this manner, we continue timestepping forward.
For specifics on the precise implementation of the AE method, we refer
the reader to appendix \ref{appendix:recipe}.

%%%%%%%%%%%%
%%%%%%%%%%%
% RESULTS
%%%%%%%%%%%
%%%%%%%%%%%%
\section{Results}
\label{sec:results}

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/nu_v_time.png}
\caption{Here we compare the time evolution of the mean temperature and the
Nusselt number in SE (a) and AE (b) for the simulations shown in 
Fig.~\ref{fig:time_trace}. The mean value of Nu (black) is shown vs. time in both
panels, and a centered boxcar moving average with a span of 50 freefall time
units is overplotted as a thick, dashed line.  The mean value of the temperature
(blue) is overplotted. We see that the mean value of Nu rapidly approaches its
mean equilibrium value (plotted as a dashed horizontal black line), signifying
that the convective motions roughly reach a statistically stationary state quickly
compared to the temperature profile, which takes much longer to trend towards its
equilibrium value. Regardless, we see that the fluctuations of Nu about the mean
value are much smaller in the final equilibrated state than in the early state
which is not in thermal equilibrium, and that the post-AE flows capture this
proper Nu amplitude variation.
The times at which AE solves occur are denoted by arrows in (b),
and the grey boxed region is examined in more detail in Fig. \ref{fig:oscillating_plumes}.
\label{fig:nu_v_time} }
\end{figure}

We study evolved standard evolution (SE) solutions whose supercriticalities ($S$) are 
$S \in (1, 10^5]$ in 2D and $S \in (1, 10^4]$ in
3D. We compare their properties to
accelerated evolution (AE) runs at $S \in (1, 10^7]$ in 2D and
$S \in (1, 10^4]$ in 3D.
We refer the reader to appendix \ref{appendix:run_table} for a full list of
simulations.

The Nusselt number (Nu) quantifies the efficiency of convective heat transport
and is defined as
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
\end{equation}
where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
The time evolution of Nu in AE and SE is compared to the mean temperature evolution
in Fig.~\ref{fig:nu_v_time}. The mean value of Nu evolves towards its final value
rapidly compared to the mean temperature, as shown by the thick, dashed moving
average.  As a result, if one is primarily measuring the mean value of Nu in
a convective system, a full SE run through $t_\kappa$ or the AE procedure may not
be necessary (e.g., \cite{stevens&all2010}). 
Regardless, the variations around the mean value in Nu do change significantly
over the course of thermal equilibration (Fig.~\ref{fig:nu_v_time}a). At early
times, variations in Nu about the mean are much larger than they are at later times,
and the use of AE seems to progress the fluctuations in Nu about the mean to
a state which is consistent with the equilibrated SE fluctuations.

When $S < 10^{3.67}$ in 2D and for all runs in 3D, 
the evolved system is characterized by a time-stationary value of Nu, and is thus
in a state of constant convective heat transport.
At larger $S$ in 2D, the value of Nu varies significantly over time even in the
equilibrated state,
as shown by the time traces for $S = 10^5$ (top, left) and $S = 10^7$ (bottom, left) for two
AE runs in Fig.~\ref{fig:oscillating_plumes}. We find that these systems exhibit
large Nu during
states in which temperature fluctuations travel in their natural buoyant
direction (Fig.~\ref{fig:oscillating_plumes}, Ia \& IIa, where cold elements fall and hot elements rise).
However, when wrongly-signed temperature perturbations are entrained in an upflow or downflow
with oppositely signed fluid, Nu is suppressed (Fig.~\ref{fig:oscillating_plumes}, Ib and IIb, 
where warm fluid is pulled down by the downflow
lane, and cool fluid is drawn up by the upflow lane). High-transport and 
low-transport states exhibit smaller Nu fluctuations away from the 
mean once the system reaches thermal equilibrium (Fig. \ref{fig:nu_v_time}).
The plumes in these
systems naturally oscillate horizontally over time, switching between transport being dominated
by a counterclockwise cell, as pictured in Fig.~\ref{fig:oscillating_plumes}, and
a clockwise cell. Our choice of no-slip
boundary conditions prevents the fluid from entering a full domain shearing state 
\cite{goluskin&all2014}, and the
oscillatory nature of the plumes is stable. However, thanks to our choice of periodic
boundary conditions and despite the no-slip conditions, the full system of the
upflow and downflow plumes is free to slowly migrate to the left or right over time,
and we observe this phenomenon in our solutions.
The 2D SE simulations exhibit the same horizontally
oscillatory behavior as the AE solutions for the same initial conditions. 
This time-dependent behavior of Nu is not seen strongly in our 3D solutions,
however most 3D simulations we conducted were at low $S$ compared to the runs in
which this behavior was observed in 2D.
